Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-15 writeup/gz_hubble_data.tex
Amend description of GZ4. Closes #101.

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of
AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
an overly restrictive cut on blended and/or saturated objects. The main GZH
site collected data until its replacement, the Galaxy~Zoo:~CANDELS project,
began on 10~Sep~2012. Classifications for the GOODS 5-epoch images were
separately obtained with the fourth version of the
site\footnote{\url{http://www.galaxyzoo.org}} from Mar-Jun 2015. The GZH
project had a total of 10,349,357~classifications from 93,898 registered
participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

>>>>

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of
AEGIS/GEMS/GOODS images mistakenly excluded from the original sample based on
an overly restrictive cut on blended and/or saturated objects. The main GZH
site collected data until its replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on
the fourth version of the Galaxy~Zoo site. The GZH project had a total of
10,349,357~classifications from 93,898 registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.
